Performance benefits of Intel\textsuperscript{\textregistered}~Optane\texttrademark~DC persistent memory for the parallel processing of large neuroimaging data

### 2019-12-17 paper.tex
added some additional comments

>>>>

\subsection{Other comments}

Storage performance when scaling the application from 25 to 96 cores could have been improved using a
NUMA-aware application, since memory is tied to the CPUs. Should a task requiring memory
stored on one CPU socket be sent to another CPU, this would incur some overheads, reducing overall application
and storage performance. Furthermore, Intel optimized Python and NumPy libraries could have been used to improve 
performance.

While these experiments may not accurately reflect the maximum performance of the storage devices for the applications,
they are meant to reflect the performance that would be obtained by the average neuroimaging researcher
executing standardized tools on infrastructure made available to them.
